Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-05-03 src/tex/ms.tex
Add Acknowlegment

Since we know intrinsic parameters play an important role in the ansatz, we
would like to investigate how intrinsic parameters affect the recalibration
process. First, we plot the parameter space of $q$ vs. $\chi_{\mathrm{PN}}$ in
Fig. \ref{fig:ps_q148_qchi}. We can see near non-spinning waveforms demonstrate

more consistent improvement, since the ansatz are developed base on non-spinning 
waveforms. Also, the original coefficients were fitted using NR waveforms with
equal or similar spin, hence the model prefers waveforms with similar spin. On 
the other hand, spinning waveforms can either improve or worsen in terms of 
mismatch base on their intrinsic parameters. To further discuss the behavior of 
non-spinning waveforms, we plot the parameter space of $\chi_1$ vs. $\chi_2$ in
Fig.~\ref{fig:ps_q148}. Waveforms along the diagonal axis, i.e. 
$\chi_1\approx\chi_2$, show good mismatch improvements as discussed above. 
Meanwhile, the top-left ($\chi_1<0$ and $\chi_2>0$) and bottom-right ($\chi_1>0$ 
and $\chi_2<0$) regions respond to optimization differently. In the top-left region, waveforms
generally improve with along optimization. However, mismatches in the bottom-right 
region do not improve after optimization. Most waveforms even turned worse after 
optimization.

@@

\begin{figure}[t]
	\script{ps_q148_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_quadrants.pdf}
	\caption{Parameter space of testing waveforms. Each region is fitted independently. Colorbar

	represents log difference of mismatches before and after optimization.}
	\label{fig:ps_q148_quadrant}
\end{figure}

@@

%\begin{enumerate} \item Comparison with the original paper is not the same.
%   (Different waveforms, different ways to modify the waveform, different range
%   of frequencies) \item More waveforms are taken so it should be more robust,
%   since the parameter space coverage is better. \item Problems with IMRPhenomD
%   model, i.e. $\chi_{\mathrm{eff}}$ reduces the dimension of spin space
%   $\chi_1, \chi_2$, so the model is flawed. Comparison issues. (Caveat) \item
%   Can in principle split parameter space into regions that can be separately
%   optimized. If not, then its must be the model's problem. Would the region
%   classification be made automatic. Are there any algorithms to do so? \item
%   Future work (Repeat on other GW models. Mapping between NR surrogate to see
%   any systematics.) \end{enumerate}

@@

\bibliography{bib}

>>>>

Since we know intrinsic parameters play an important role in the ansatz, we
would like to investigate how intrinsic parameters affect the recalibration
process. First, we plot the parameter space of $q$ vs. $\chi_{\mathrm{PN}}$ in
Fig. \ref{fig:ps_q148_qchi}. We can see near non-spinning waveforms demonstrate
more consistent improvement, since the ansatz are developed base on non-spinning 
waveforms. Also, the original coefficients were fitted using NR waveforms with
equal or similar spin, hence the model prefers waveforms with similar spin. On 
the other hand, spinning waveforms can either improve or worsen in terms of 
mismatch base on their intrinsic parameters. To further discuss the behavior of 
non-spinning waveforms, we plot the parameter space of $\chi_1$ vs. $\chi_2$ in
Fig.~\ref{fig:ps_q148}. Waveforms along the diagonal axis, i.e. 
$\chi_1\approx\chi_2$, show good mismatch improvements as discussed above. 
Meanwhile, the top-left ($\chi_1<0$ and $\chi_2>0$) and bottom-right ($\chi_1>0$ 
and $\chi_2<0$) regions respond to optimization differently. In the top-left region, waveforms
generally improve with along optimization. However, mismatches in the bottom-right 
region do not improve after optimization. Most waveforms even turned worse after 
optimization.

@@

\begin{figure}[t]
	\script{ps_q148_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_quadrants.pdf}
	\caption{Parameter space of testing waveforms. Each region is fitted independently. Colorbar
	represents log difference of mismatches before and after optimization.}
	\label{fig:ps_q148_quadrant}
\end{figure}

@@

@@

We thank Will M.~Farr, Max Isi, and Mark Hannam for helpful discussions; we also
thank Carl-Johan Haster, Neil J.~Cornish and Thomas Dent for comments on the
draft. The Flatiron Institute is a division of the Simons Foundation. T.E.\ is
supported by the Horizon Postdoctoral Fellowship.
\bibliography{bib}
